\section{Remote-controlled Home Robot Server with ZigBee Sensor Network}
Recently, interest of general public toward ubiquitous home network has immensely increased and wireless PAN (personal area network) has attracted strong attentions as short-distance networking solution. Convenience of wireless PAN technology has attracted more attentions over traditional wired home network devices such as Ethernet, PLC and Home PNA since it requires no cabling work. In the future, home server will be combined with robot to provide functionalities identical to current home service robot as well as to implement more effective and spontaneous server. In this paper, embedded board has proposed as a home server for an efficient control of internal information and conditions of house from remote location and virtual home robot server to be implemented with ZigBee sensor network \cite{4108460}.

\section{Remote power On\/Off control and current measurement for home electric outlets based on a low\-power embedded board and ZigBee communication}
Zigbee is a wireless network that any device can connect to and interact with other devices that is also connected to it. Zigbee is known for being security assistance for residences and the future of smart homes. An example of that is came up with an idea to remotely control on and off switches and at the same time measure the current for electric outlets at home \cite{4559539}. They used two modules which are the server and zigbee control modules. For their interface they have used visual basic to generate a simple GUI for the user.

\section{Design of Intelligent Mobile Monitor System Based on ZigBee and Android}
Aside from zigbee another significant component the group planned to work with is android. Android can be used as our interface to communicate with the zigbee controlled car. Chang-qing \& Hai-liang introduced a design for an intelligent car that uses bluetooth as to connect with any smartphone \cite{chang2012design}. The only difference is the medium used for the interaction of the car and the user. Zigbee working together with android is not new. Dao designed an intelligent mobile monitor system using zigbee network and android platform. The mobile monitor system has high stability and high reliability and also flexible because it can be used in any environment whether in the agriculture, industry or for service business \cite{QuDao2012}.  

\section{SMaRTCaR: an integrated smartphone-based platform to support traffic management applications}
A research conducted by Campolo uses a smartphone as a platform to control a car and support traffic management \cite{6398700}. This is to add new services for the passengers and drivers. They have studied that with the growing technology and that smartphone is one of the most useful for experiment. Also they recognized that cars can be the most efficient way to collect data through surroundings. Sensors are installed in the cars to monitor parameters like temperature and amount of pollution. 

\section{Design and Construction of Rescue Robot and Pipeline Inspection Using Zigbee}
Finding a technique to help, a robot was used to rescue a trapped baby in a bore well. The robot was also controlled by human and acts by the instruction given to it. By using just pc and the technology of wireless called zigbee, they are able to manipulate the mobile robot. They also use a camera for monitoring the audio and video \cite{Bharathi2013}.

\section{Mobile robots in mine rescue and recovery}
In other areas such as in mining, accidents also occur. Accidents like being trap underground are some usual cases in the United States. The country provides rescue teams that are trained for dangerous rescue missions. Using robots, they gather data from the hazardous areas and at the same time search for missing humans. Using robotics as a solution prevents other accidents to happen like detonating explosives and also suffer from heavy smokes and unstable ground \cite{5069840}.

\section{Multi-robot exploration under the constraints of wireless networking}
Some other benefits of monitoring robot are for surveillance, planetary explorations and some rescue missions. Using robotics can make dangerous jobs easy by being much faster and robust. The approach to create multi-robot exploration takes away limitations of the wireless networking. The built algorithm is based on a population that makes samples of all the movement of robots. Also this algorithm selects the best one every step. The created team of robots explores the field maintaining the connection of the ad hoc network within each robot as well in their base located at a fixed point \cite{Rooker2007}.

\section{ROBHAZ-rescue: rough-terrain negotiable teleoperated mobile robot for rescue mission}
A designed a robot for rescue operations named ROBHAZ-DT3 operated with chained double\-track mechanisms. The main purpose is to work for military and civilian missions located in hazardous and dangerous environments. They build the algorithm based on effectiveness of the robot on the field and how will it perform the rescue operation \cite{1501248}.

\section{Remote control realization of distributed rescue robots via the wireless network}
The wireless sensor network (WSN) is quickly being developed and it can result to many possibilities. Integrating the new wireless technology zigbee to mobile robots is their focus. Some achievements are being remotely controlled and monitoring different sensing devices with 802.11g and zigbee. Communication between human and robot is very significant. With the use of 802.11 g the voice signals and transmitting video are further enhanced to effectively detect the victims \cite{4655164}.

\section{Design and implementation of user-friendly remote controllers for rescue robots used at fire sites}
Many conducted and developed robots for rescue operations during catastrophe and these generated different types of robots like fire\-fighting robots, surveillance and the rescue robots. They propose a similar only a more user-friendly type of robot that is used for gathering information about like videos and concentration of temperature and gas data \cite{5649481}.  